Status of nuclear optical potentials and future prospects

### 2019-07-02 Notes/Candidacy/Paper/candidacy_paper.tex
Update to candidacy notes
Added bullet points for outlining candidacy paper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% File: candidacy_paper.tex
%
% Author: A. J. Tropiano (tropiano.4@osu.edu)
% Date: July 1, 2019
%
% Candidacy paper on the status of nuclear optical potentials and future prospects.
%
% Revision history:
% 	xx/xx/xx --- ...             
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Start text here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Section 2}
\label{sec:section_2}

Start text here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Section 3}
\label{sec:section_3}

Start text here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Section 4}
\label{sec:section_4}

Start text here.

@@

Summary and outlook. Example citation \cite{Rotureau:2016jpf}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% File: candidacy_paper.tex
%
% Author: A. J. Tropiano (tropiano.4@osu.edu)
% Date: July 1, 2019
%
% Candidacy paper on the status of nuclear optical potentials and future prospects.
%
% Revision history:
% 	07/02/19 --- Starting with bulleted outline. 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Things to include:
\\
-- r-process for motivation.
\\
-- Include multiple scattering, self-consistent Green's function methods.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Phenomenology of optical potentials}
\label{sec:section_2}

Things to include:
\\
-- Form of the potential: Woods-Saxon shape, coulomb component, spin-orbit force.
\\
-- Fit strength, radii, and diffuseness of complex potential.
\\
-- Issue: fitting ambiguities, extractions to exotic regions of the nuclear chart.
\\
-- Make sure to touch on phenomenology of optical potentials in modern experimental analyses (key word is modern!)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Ab initio optical potentials}
\label{sec:section_3}

Things to include:
\\
-- Successes and limitations.
\\
-- Motivation: predictions for exotic region of the nuclear chart.
\\
-- Coupled cluster Green's function \cite{Rotureau:2016jpf}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Theoretical issues}
\label{sec:section_4}

Things to include:
\\
-- Fitting ambiguities for phenomenological potential.
\\
-- Uncertainty quantification.

@@

Summary and outlook.
